Score-based tests in lavaan 0.5-18

### 2015-08-14 constraints/lav_constraints.Rmd
more detail on lavaan's new constraints
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@384 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

>>>>

```{r}
## comparison, solution?
## gradient of likelihood, which is (- LM term)
lavInspect(restr, "gradient")
## matches scores
lsc <- lavScores(restr)
colSums(lsc)/nobs(restr)

lsc2 <- t(lavInspect(restr,"gradient") + t(lsc))

lavsc2 <- function(fit, ...){
  t(lavInspect(fit,"gradient") + t(lavScores(fit)))
}

lavinfo <- function(fit, ...) lavInspect(fit, "information")

sctest(restr, order.by=yg$agegroup, parm=c(1,16,46,61,76), scores=lavsc2, vcov=lavinfo, 
       sandwich=FALSE, functional="LMuo")

## find parameters affected by equality constraints
apply(restr@Model@ceq.JAC==0,2,all)
## find redundant parameters (only one non-zero entry, but
## not for a+b+c == 3)
apply(restr@Model@ceq.JAC!=0,2,sum)

## use qr() to find non-redundant parameters?
```
